### 2021-07-21 doc/thesis/chapters/hls.tex
skip the Functionality section
state of the art HLS

- usage in percentage (market share), compared to direct RTL coding\\

-  Language Support\\
\cplusplus and SystemC\\
In the latest Xilinx HLS tools 'Vitis HLS' and 'Vivado HLS', the language SystemC is already deprecated \cite{VivadoHlsSystemC}.\\

- efficiency (see \cite[II.C.: State of the Art]{CompareHlsVHDLArticle})\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Functionality}

transform high-level code to HDL.\\
-analysis\\
-scheduling\\
-pipelining\\

- Limitations\\
dynamic memory allocation, etc.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compiler Directives (\#pragma's)}

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data types}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional statements}

>>>>

Information for this section is found in \cite{EvolutionOfHLS}, \cite{XilinxVivisHLSOpenSource} and \cite{CompareHlsVHDLArticle}.\\

HLS has been developed over 20 years ago, but has not been able to replace the manual, traditional implementation of RTL, using VHDL and Verilog, so far.
Unfortunately, no published numbers about the market share of HLS in relation to traditional implementations could be found during the research in this thesis.
However, according to the given sources it is becoming more and more popular in recent years.
This is mainly based on the fact that the HLS tools keep producing results of better quality as they are developed further.
This especially regards the efficiency of the produced RTL code, the useability of the tools, as well as the better understandable correlation between the high-level code and the generated RTL code.\\

Xilinx is the largest manufacturer of FPGAs globally and therefore its tool 'Xilinx HLS' is widely used.
Intel, the second largest FPGA manufacturer, also has its HLS tool called 'Intel oneAPI' \cite{IntelHLSOneAPI}.
Both companies are conducting serious effort to push the HLS implementation method.
Xilinx recently open-sourced the code for the front-end of their HLS compiler.
The front-end processes the HLS code, specifically \cplusplus, and creates an intermediate representation from it.
The company expects to expand the community engagement and the encouragement of innovation, driven by users, with this step.
Also Intel with its oneAPI toolkit is trying to introduce a wider usage of HLS to the community.\\

In terms of language support, several tools settle for \cplusplus.
Intel oneAPI uses library APIs and DP\cplusplus\ (Data-Parallel \cplusplus), which is an extension to the ISO \cplusplus\ standard.
Xilinx also decided in favor of the \cplusplus\ language for their tools 'Vivado HLS' and 'Vitis HLS'.
In older versions, SystemC was supported for synthesis as well, but is now deprecated in the respective latest versions \cite{VivadoHlsDeprecatesSystemC}.\\

Summing up, HLS is gaining more and more attention as it becomes more efficient.
Its usage is being promoted and pushed forward with serious effort by the major FPGA chip manufacturers and tool vendors.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Functionality}
%
%transform high-level code to HDL.\\
%-analysis\\
%-scheduling\\
%-pipelining\\
%
%- Limitations\\
%dynamic memory allocation, etc.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Compiler Directives}

e.g. \#pragma's

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Data Types}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Conditional Statements}

### 2021-07-21 doc/thesis/chapters/system-architecture-and-concept.tex
state of the art HLS

\begin{itemize}
  \item \textbf{GNU Radio}\\
      GNU Radio is a free and open-source software development toolkit to implement a software-defined radio.
      The implementation is done by connecting functional blocks in a block design.
      This abstracts the inner workings of each functional block and thus provides an implementation approach on a very high level of abstraction.
      GNU Radio supports interfaces to external RF hardware \cite{SoftwareGnuRadio}.
  \item \textbf{Matlab}\\
      Matlab is a software platform that can work with matrices and compute numerical solutions.
      Matlab also includes various toolboxes, that support developers with complex calculations and tasks on datasets.
      This includes a range of toolboxes for signal processing, such as filter designers or FFT functions, as well as convenient ways to visualize data \cite{SoftwareMatlab}.
  \item \textbf{FPGA: \cplusplus\ High-Level Synthesis}\\
      In order to use an FPGA, a hardware design needs to be developed for it.
      This can be done using high-level synthesis.
      High-level synthesis (HLS) is explained in detail in Chapter \ref{cha:HLS}.
  \item \textbf{FPGA: VHDL}\\
      Similar to the HLS approach, this is a variant to write a hardware design for an FPGA.
      The language VHDL is used in this approach.
\end{itemize}

>>>>

\begin{itemize}
  \item \textbf{GNU Radio}\\
      GNU Radio is a free and open-source software development toolkit to implement a software-defined radio.
      The implementation is done by connecting functional blocks in a block design.
      This abstracts the inner workings of each functional block and thus provides an implementation approach on a very high level of abstraction.
      GNU Radio supports interfaces to external RF hardware \cite{SoftwareGnuRadio}.
  \item \textbf{Matlab}\\
      Matlab is a software platform that can work with matrices and compute numerical solutions.
      Matlab also includes various toolboxes, that support developers with complex calculations and tasks on datasets.
      This includes a range of toolboxes for signal processing, such as filter designers or FFT functions, as well as convenient ways to visualize data \cite{SoftwareMatlab}.
  \item \textbf{FPGA: \cplusplus\ High-Level Synthesis}\\
      In order to use an FPGA, a hardware design needs to be developed for it.
      This can be done using high-level synthesis.
      This thesis focuses in \cplusplus and does not implement a SystemC variant, because Xilinx has deprecated SystemC support for synthesis in their latest HLS tools.
      This, and the details of High-level synthesis (HLS) are explained in Chapter \ref{cha:HLS}.

  \item \textbf{FPGA: VHDL}\\
      Similar to the HLS approach, this is a variant to write a hardware design for an FPGA.
      The language VHDL is used in this approach.
\end{itemize}
